My title

### 2024-12-03 paper/paper.qmd
changed to linear regression model

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

>>>>

@fig-vendorsales shows the number of sales provided on egg dozens, showing a large variation between vendors. Metro notably had the most egg discounts, and Galleria the least.

```{r}
#| label: fig-vendorsales
#| fig-cap: Number of Discounts Provided By Each Vendor On Eggs Between March and November 2024
#| echo: false
#| warning: false
#| message: false

analysis_data |> 
  ggplot(aes(x = vendor)) +
  geom_bar() +
  theme_classic() +
  labs(x = "Vendor",
       y = "Number of Sales")
```

@@

The goal of our modeling is to understand how the predictor variables — month, vendor, presale price, and previous month's average sale price — affects the response variable of current price. For this paper, a multiple linear regression model will be utilized.

@@

Define $y_i$ as the current price. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
